### 2014-03-07 docs/related-work.tex
Fix file format
Winter paper.

\documentclass{article}  usepackage{url}

@@

There are a few approaches proposed to address the problem of proxy diversity.
Flash proxy~\cite{flashproxy-pets12} attempts to address the problem  by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing and
difficult to block. Their approach to proxy unblockability is in a sense
opposite to this work's: where flash proxy uses many, cheap, unreliable proxies,
we use just one high-value proxy, to block which would cause expensive
collateral damage. There exists a prototype transport that combines flash proxy
with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
possible to obfuscate flash proxy's outermost WebSocket layer. Decoy routing is
a recently proposed approach for proxy diversity. Telex~\cite{telex} is an
instance of circumvention systems that leverages decoy routing. Telex relies on
friendly ISPs that deploy Telex stations on paths between censors' networks and
popular, uncensored Internet destinations. Telex stations would divert the
seemingly  innocuous flows to a forbidden site if a special ``tag'' is
presented. Telex will prevail only if a large number of ISPs are cooperative and
willing to deploy such stations. A recent study~\cite{nodirectionhome} on ASes
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable if ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of. \\

@@

>>>>

\documentclass{article}  
\usepackage{url}

@@

There are a few approaches proposed to address the problem of proxy diversity.
Flash proxy~\cite{flashproxy-pets12} attempts to address the problem  by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing and
difficult to block. Their approach to proxy unblockability is in a sense
opposite to this work's: where flash proxy uses many, cheap, unreliable proxies,
we use just one high-value proxy, to block which would cause expensive
collateral damage. There exists a prototype transport that combines flash proxy
with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
possible to obfuscate flash proxy's outermost WebSocket layer. Decoy routing is
a recently proposed approach for proxy diversity. Telex~\cite{telex} is an
instance of circumvention systems that leverages decoy routing. Telex relies on
friendly ISPs that deploy Telex stations on paths between censors' networks and
popular, uncensored Internet destinations. Telex stations would divert the
seemingly  innocuous flows to a forbidden site if a special ``tag'' is
presented. Telex will prevail only if a large number of ISPs are cooperative and
willing to deploy such stations. A recent study~\cite{nodirectionhome} on ASes
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable if ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.\\

@@

Winter and Lindskog~\cite{foci12-winter} investigated how China's Great Firewall blocks Tor.
They confirmed an earlier discovery of Wilde~\cite{wilde} that the firewall identifies Tor relays using more than passive monitoring:
it actively probes destination addresses to see if they speak the Tor protocol, and if so,
blocks them for the future.
(At the time, the firewall identified connections for future probing by looking for a distinctive
list of ciphersuites sent by a Tor client in its TLS client hello.) %\cite{bug4744}
The discovery of active probing was the motivation for probing resistance in ScrambleSuit.
\\
